\chapter{Introduction}
% DELETE THE TEXT BELOW
In this first chapter we expect you to introduce the project explaining what the project is about, what is the final goal, what are the topics tackled by the project, etc.\newline The introduction must not include any low-level detail about the project, avoid sentences written like: we did this, then this, then this, etc.\newline It is strongly suggested to avoid expressions like `We think`, `We did`, etc...it is better to use impersonal expressions such as: `It is clear that`, `It is possible that`, `... something ... has been implemented/analyzed/etc.` (instead of `we did, we implemented, we analyzed`).\newline In the introduction you should give to the reader enough information to understand what is going to be explained in the remainder of the report (basically, expanding some concept you mentioned in the Abstract) without giving away too many information that would make the introduction too long and boring.\newline Feel free to organize the introduction in multiple sections and subsections, depending on how much content you want to put into this chapter.

Remember that the introduction is needed to make the reader understand what kind of reading he or she will encounter. Be fluent and try not to confuse him or her.
The introduction must ALWAYS end with the following formula: The remainder of the document is organized as follows. In Chapter 2, ...; in Chapter 3, ... so that the reader can choose which chapters are worth skipping according to the type of reading he or she has chosen.
